Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-28 GWLDCII.tex
read 4.6 to end of section

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}. Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.

@@

The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}. Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.

@@

Also $u$ cannot be $n-4$, for the following reason. By Remark~\ref{rmk cyclic} we know that $I_{n-1}^W(q) = n-5$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign. Thus $n-4 \not\in I_{n-1}^W$, and since $I_{n-1}^W = I_n^V\cup\{n-1\}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.

@@

  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$. If $n-2$ supports no propagators in $V$ then certainly no plusses appear in the $n-2$ column of the Le diagram of $V$. If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well. By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.

  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path in the Le diagram of $V$ from some vertical edge $i$ to the bottom edge $n-3$.  In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path starting at it (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.  By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$. All other paths are unchanged.

   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
\end{proof}

@@

Note that by Remark \ref{rem n-2 case}, we only need to consider when $W$ is a diagram with one of the two configurations depicted in Figure~\ref{fig special p}, and if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well. Let $V$ be $W$ with $p$ removed.

@@

 The pairing is defined as follows:
  \begin{itemize}
  \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
  \item Every square containing in a plus in the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
  \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column. If $n-4 \not\in I_1^V$ then pair this plus with the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then pair it with the $(n-5) \rightarrow n$ plus in $W$.

>>>>

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}. Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}. Other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}. Specifically, Marcott shows that the space parametrized by the Wilson loop diagrams is  exactly the correct positroid cell in $\Gr(k,n)$, up to a set of measure $0$ \cite{WLDdim}.

@@

The matrix $C(W)$ defines a positroid cell associated to $W$ in the positive Grassmannian $\Gr(n, |\cP|)$, which we denote by $\Sigma(W)$ \cite{wilsonloop}. Marcott \cite{WLDdim} shows that  the matrix $C(W)$ parametrizes a space whose close is exactly the closure of $\Sigma(W)$. That is, the space defined by $C(W)$ and the cell $\Sigma(W)$ agree up to a set of measure $0$. Most of the work in this paper, and in \cite{generalcombinatoricsI} focuses on characterizing the positroid cell associated to each Wilson loop diagram $W$.

@@

Also $u$ cannot be $n-4$, for the following reason. By Remark~\ref{rmk cyclic} we know that $I_{n-1}^W(q) = n-5$, leaving no propagators supported on $n-4$ for $I_{n-1}^W$ to assign. Thus $n-4 \not\in I_{n-1}^W$. Since $I_{n-1}^W = I_n^V\cup\{n-1\}$ by Lemma~\ref{lem I}, we cannot have $n-4$ in $I_n^V$ either.

@@

  If $n-3\in I_{k}^{V}$ then $I_k^V$ must contribute a plus in the $n-3$ column of the Le diagram of $V$, and by Lemma~\ref{lem I} we have $I_{k}^{W} = I_k^{V}\cup \{n-2\}$. If $n-2$ supports no propagators in $V$ then no plusses appear in the $n-2$ column of the Le diagram of $V$. If $n-2$ supports at least one propagator in $V$ then $n-2 \in I_{n-2}^V$ and so by hypothesis $n-1 \in I_{n-2}^V$ as well. By Lemma~\ref{lem n-2 bad}, the only necklace element of $V$ containing $n-2$ is $I_{n-2}^{V}$ and \hlfix{the corresponding plus is not contributed to the Le diagram of $W$ by $I_{n-2}^{W}$.}{Lemma {\ref{lem n-2 bad}} point 4 says that  $I_{n-2}^W$ contributes a + in the n-2 column and point 3 says that $I_{n-2}^W$ contributes a + in the n-2 column. Are we talking about $n-1$ column?}

  Since $n-3 \in I_k^V \setminus I_1^V$, we must have a path in the Le diagram of $V$ from some vertical edge $i$ to the bottom edge $n-3$.  In the Le diagram of $W$, the index $n-3$ labels a vertical edge with no path \hlfix{starting at it}{coming from $I_k^W$. There are 3 paths starting here in the Le diagram as a whole} (since $n-3$ belongs to both $I_1^W$ and $I_k^W$), and there must be a path leading to $n-2$ since $n-2 \in I_k^W \setminus I_1^W$.  By the previous paragraph no other path from $I_k^V$ could end at $n-2$, and since the paths cannot cross we conclude that the $i\rightarrow (n-3)$ path in the Le diagram of $V$ must become a $i\rightarrow (n-2)$ path in the Le diagram of $W$. All other paths are unchanged.

   Thus the plus contributed by $I_k^V$ in the $n-3$ column of the Le diagram of $V$ is shifted into the $n-2$ column in the Le diagram for $W$, where there was no plus before, and no other plusses are changed.
\end{proof} \todo{I am still very confused by this proof, possibly due to my misunderstanding of first highlighted comment}

@@

We consider the two cases of propagator configurations $W$ depicted in Figure~\ref{fig special p}.  Note that by Remark \ref{rem n-2 case}, we need only consder the situation that if $n-2 \in I_{n-2}^V$ then $n-1 \in I_{n-1}^V$ as well. Let $V$ be $W$ with $p$ removed.

@@

 The pairing is defined as follows:
  \begin{itemize}
  \item The plusses in the $\mathcal{B}$ region of both Le diagrams are identical, so each plus in this region is paired with itself.
  \item Every square containing a plus in the leftmost two columns (the $n$ and the $n-1$ columns) of $\mathcal{A}$ for $V$ also contains a plus in $W$, so these plusses are also paired with themselves.
  \item The plusses in the $n-3$ column for $V$ are paired with the corresponding plusses in the $n-2$ column for $W$.
  \item If there is a plus in the $n-2$ column of $\mathcal{A}$ in $V$ then Lemma~\ref{lem n-2 bad} applies, so there is exactly one such plus in this column. If $n-4 \not\in I_1^V$ then pair this plus with the $(n-5)\rightarrow (n-1)$ plus in $W$, whereas if $n-4 \in I_1^V$ then pair it with the $(n-5) \rightarrow n$ plus in $W$.
